Comparing Power Optimizations in the Reorder Buffer

### 2011-06-07 paper/paper.tex
paper

\maketitle
\begin{abstract}
	In an effort to increase instruction level parallelism techniques such 
as pipelining, out of order execution and operand forwarding.  However 
these efforts come at a large power cost.  Out of order execution requires
a ReOrder Buffer (ROB), to commit the registers in program order.  This 
structure has grown to be monolithic numerous entries and read/write ports.
There is no current methods to efficiently and equally compare various
ROB advancements to improve power efficiency.  
\end{abstract}

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging} % NOT required for Proceedings

\section{Introduction}
BLAH BLAH BLAH INTRO WEEEE

@@

\subsection{Model Implementation}
\subsubsection{Circular ROB}
\subsubsection{Distributed ROB}
\subsubsection{Dynamic ROB}
\subsubsection{Reduced Output Port ROB (Retention Latch)}
\subsection{Power Tabulation Implementation}
\section{Results}
hi
\subsection{subsection titl}
sub section.. with table!
\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

>>>>

\maketitle
\begin{abstract}
	In an effort to increase instruction level parallelism techniques such 
as pipelining, out of order execution and operand forwarding.  However 
these efforts come at a large power cost.  Out of order execution requires
a ReOrder Buffer (ROB), to commit the registers in program order.  This 
structure has grown to be monolithic with numerous entries and read/write ports.
There is no current methods to efficiently and equally compare various
ROB advancements to improve power efficiency. We propose a loosely clycle
accurate model that keeps track of the power usages of the ROB.  Using the 
simulation tool, we are able to compare and contrast the affects of improvements
made on the ROB.  This also allows for a first line test to validate proof of 
concepts for future power efficient ROB designs. 
\end{abstract}

\terms{Power, Energy, Architecture}

\keywords{Power efficiency, ROB, Simulation} % NOT required for Proceedings

\section{Introduction}
BLAH BLAH BLAH INTRO WEEEE
\section{Background}
    An out of order execution system has two additional stages 
to the lifetime of the instruction on top of the traditional pipeline 
stages.  Each of which a small memory array to keep track of instuction flow.
The first addtion, the instruction queue(IQ) which holds instructions that are 
waiting to be executed.  Each entry will hold the instruction -- including 
type, operand registers, and destination registers.  The second structure 
holds the instructions that are in flight but not yet commited to the register
file. Each entry will hold both PC of the instruction, as well as the destination
register and the result of the excution unit.  There is also a flag that will
mark the result of the entry as valid.

Replacing the traditional instruction dispatch stage, An placeholder will be made for the 
instruction in ReOrder Buffer (ROB), and the instructions will be placed
in the instruction queue(IQ). In this stage instructions will first wait for their operands if not already
available.  When all operands are available, the instruction is ready to 
be executed so wait until its appropriate execution unit is free.  At this 
point the instruction exits the IQ and begins execution.

Upon execution completion, the output value is stored in the ROB with its 
corresponding entry and that entry is marked as valid or completed with a 
1 bit flag.  An entry is commited from the ROB to the architectrual register
file (ARF) when that entry is the oldest (lowest PC) and its result has been 
marked as valid. 
\subsection{Circular ROB}
The circular ROB is 
\subsection{Latch ROB}
\subsection{Dynamic ROB}
\subsection{Distributed ROB}

@@

\begin{tabular}{|c|c|c|c|c|} \hline
ins\_profile&default\_profile&173.applu&191.fma3d&183.equake\\ \hline
loadProc&0.10&0.32&0.12&0.37\\ \hline
storeProc&0.10&0.12&0.24&0.06\\ \hline
addProc&0.10&0.01&0.15&0.08\\ \hline
subProc&0.10&0.01&0.15&0.08\\ \hline
multProc&0.10&0.01&0.15&0.08\\ \hline
divProc&0.10&0.01&0.15&0.08\\ \hline
faddProc&0.10&0.13&0.01&0.07\\ \hline
fsubProc&0.10&0.13&0.01&0.06\\ \hline
fmultProc&0.10&0.13&0.01&0.06\\ \hline
fdivProc&0.10&0.13&0.01&0.06\\ \hline
forwardingRate&0.10&0.06&0.06&0.06\\ \hline
instCount&10000&10000&10000&10000\\ \hline\end{tabular}
\caption{Benchmark Instruction Profiles}
\subsection{Model Implementation}
\subsubsection{Circular ROB}
\subsubsection{Distributed ROB}
\subsubsection{Dynamic ROB}
\subsubsection{Reduced Output Port ROB (Retention Latch)}
\subsection{Power Tabulation Implementation}
\section{Results}
hi
\subsection{subsection titl}
sub section.. with table!
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
% end the environment with {table*}, NOTE not {table}!
